Making sure the variances converge

### 2024-07-12 Two_var.Rmd
Doc to compare variances

---
title: "Monte-Carlo and bootstrap together - Part 2"
output:
  pdf_document: default
  html_document: default
date: "2024-07-11"
---

@@

# Useful functions

@@

# A function to plug bootstrap in a MC process

@@

# Test

```{r}
start.time <- Sys.time()

res <- MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)

end.time <- Sys.time()
time.taken <- end.time - start.time

time.taken
```

```{r}
cat("Mean of Monte-Carlo samples:", res[1], "\nMonte-Carlo variance:", res[2], "\nMean of the variance of bootstrap samples:", res[3])
```

>>>>

---
title: "Making sure the variances converge"
output: html_document
date: "2024-07-12"
---

@@

```{r}
# Sample size
n <- 1000
```

# Monte Carlo alone

10 000 Monte Carlo iterations would be fine

```{r}

```

# Bootstrap for each Monte Carlo iteration

1 000 Monte Carlo iterations should be fine
400 bootstrap iterations for each would be fine (200 to begin with if it is too much)

@@

@@
